Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2012-03-07 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2012:03:07	14:10:10	(Wed 7.Mar)

\begin{itemize}
\item Why beamforming?
\item Adaptive beamformers
\item Challenges in active sonar systems. Correlated noise, robustification kills the adaptive potential. Quite computationally intensive.
\item LCA is like DAS, only we test several windows and choose the one that yield the lowest beamformer output power. Ultrasound \cite{Synnevag2008}, active sonar 
\end{itemize}

>>>>

\begin{itemize}
\item Why beamforming?
\item Adaptive beamformers
\item Challenges in active sonar systems. Correlated noise, robustification kills the adaptive potential. Quite computationally intensive.
\item LCA is like DAS, only we test several windows and choose the one that yield the lowest beamformer output power. Ultrasound \cite{Synnevag2008}, active sonar \cite{Buskenes2011}\cite{Blomberg2011}\cite{Blomberg2012}
\item Outline: Start with Capon's response when means for robustification are added.
\end{itemize}

Outline:
\begin{itemize}
\item Capon's resonse 
\item Choice of window functions makes little difference.
\item Steering and mainlobewidths have outer bounds.
\item Beamspace?
\item Chosen window plots - what may they tell us? Variance intensity values when using various windows.
\item Assymmetric windows?
\end{itemize}
